Treatment heterogeneity in comparative effectiveness of teriparatide vs bisphosphonates: multi-database cohort study

### 2021-02-28 submission/manuscript.rmd
include tiff figure
planning absolute plot

When assessing heterogeneity of treatment effect for hip fractur    e, we estimated calibrated hazard ratios of `r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "mdcr") %>% pull(hr)` (`r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "mdcr") %>% pull(lower)` to `r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "mdcr") %>% pull(upper)`; 95% CI),
`r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "optum_dod") %>% pull(hr)` (`r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "optum_dod") %>% pull(lower)` to `r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "optum_dod") %>% pull(upper)`; 95% CI) and `r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "panther") %>% pull(hr)` (`r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "panther") %>% pull(lower)` to `r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "panther") %>% pull(upper)`; 95% CI) within the highest risk quarter of MDCR, OPTUM_DOD and PANTHER respectively. This translated in absolute risk reduction of `r hipFractureAbsolute %>% filter(database == "mdcr") %>% pull(estimate)`% (`r hipFractureAbsolute %>% filter(database == "mdcr") %>% pull(lower)`% to `r hipFractureAbsolute %>% filter(database == "mdcr") %>% pull(upper)`%; 95% CI), `r hipFractureAbsolute %>% filter(database == "optum_dod") %>% pull(estimate)`% (`r hipFractureAbsolute %>% filter(database == "optum_dod") %>% pull(lower)`% to `r hipFractureAbsolute %>% filter(database == "optum_dod") %>% pull(upper)`%; 95% CI), `r hipFractureAbsolute %>% filter(database == "panther") %>% pull(estimate)`% (`r hipFractureAbsolute %>% filter(database == "panther") %>% pull(lower)`% to `r hipFractureAbsolute %>% filter(database == "panther") %>% pull(upper)`%; 95% CI). The random effects meta-analytic calibrated hazard ratio within the highest risk quarter was `r metaCalibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101) %>% pull(hr)` (`r metaCalibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101) %>% pull(lower)` to `r metaCalibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101) %>% pull(upper)`; 95% CI) across the 3 databases.

@@

\newpage
```{r plotMeta, echo=FALSE, fig.cap="This is a caption", out.width = '100%'}
knitr::include_graphics(here::here("figures/plotMeta.pdf"))
```

>>>>

When assessing heterogeneity of treatment effect for hip fracture, we estimated calibrated hazard ratios of `r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "mdcr") %>% pull(hr)` (`r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "mdcr") %>% pull(lower)` to `r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "mdcr") %>% pull(upper)`; 95% CI),
`r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "optum_dod") %>% pull(hr)` (`r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "optum_dod") %>% pull(lower)` to `r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "optum_dod") %>% pull(upper)`; 95% CI) and `r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "panther") %>% pull(hr)` (`r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "panther") %>% pull(lower)` to `r calibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101, database == "panther") %>% pull(upper)`; 95% CI) within the highest risk quarter of MDCR, OPTUM_DOD and PANTHER respectively. This translated in absolute risk reduction of `r hipFractureAbsolute %>% filter(database == "mdcr") %>% pull(estimate)`% (`r hipFractureAbsolute %>% filter(database == "mdcr") %>% pull(lower)`% to `r hipFractureAbsolute %>% filter(database == "mdcr") %>% pull(upper)`%; 95% CI), `r hipFractureAbsolute %>% filter(database == "optum_dod") %>% pull(estimate)`% (`r hipFractureAbsolute %>% filter(database == "optum_dod") %>% pull(lower)`% to `r hipFractureAbsolute %>% filter(database == "optum_dod") %>% pull(upper)`%; 95% CI), `r hipFractureAbsolute %>% filter(database == "panther") %>% pull(estimate)`% (`r hipFractureAbsolute %>% filter(database == "panther") %>% pull(lower)`% to `r hipFractureAbsolute %>% filter(database == "panther") %>% pull(upper)`%; 95% CI). The random effects meta-analytic calibrated hazard ratio within the highest risk quarter was `r metaCalibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101) %>% pull(hr)` (`r metaCalibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101) %>% pull(lower)` to `r metaCalibrateRiskStratified %>% filter(riskStratum == "Q4", stratOutcome == 101, estOutcome == 101) %>% pull(upper)`; 95% CI) across the 3 databases.

@@

\newpage
```{r plotMeta, echo=FALSE, fig.cap="This is a caption", out.width = '100%'}
knitr::include_graphics(here::here("figures/plotMeta.tiff"))
```
